KidsAIR wood stove grades and usage

### 2020-11-18 main_analysis_primary_models.Rmd
major analysis updates

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25) 
  rownames_to_column() %>% 
  #mutate(filter_outliers = if_else(rowname %in% c(57), 1, 0)) %>% 
  mutate(log_person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 2.33, log_person_time_at_risk)) %>% 
  mutate(person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 72, person_time_at_risk)) 
  #filter(lrti_incidence < 0.7) %>% 
  filter(filter_outliers == 0)

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds"))
```

@@

>>>>

analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_1obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25,
         lrti_events_di_total = as.factor(lrti_events_di_total),
         person_time_at_risk_iqr = person_time_at_risk/20) 
  #filter(gender == "Female")
  #filter(home_sqft_2level == "1500+")

analysis_data_outliers <- analysis_data %>% 
  #rownames_to_column() %>% 
  #mutate(filter_outliers = if_else(rowname %in% c(57), 1, 0)) %>% 
  mutate(log_person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 2.33, log_person_time_at_risk)) %>% 
  mutate(person_time_at_risk = if_else(area == "AK" & child_id_num == 31, 72, person_time_at_risk),
         lrti_events_total = as.factor(lrti_events_total),
         lrti_events_di_total = as.factor(lrti_events_di_total))

analysis_data_winter1 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 1)

analysis_data_winter2 <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds")) %>% 
  mutate(pm_mean_sampling_period_iqr = pm_mean_sampling_period/25,
         pm_at_home_sampling_period_iqr = pm_at_home_sampling_period/25) %>% 
  filter(person_time_at_risk_winter > 0) %>% 
  filter(winter_id == 2)
```

@@

# Final options for primary model framework

## Poisson model
```{r, echo=TRUE, eval=FALSE}
poisson_results <- glmer(lrti_events_total ~ treatment_assigned + child_age + 
                         (1 | home:cohort:area), 
                         data = analysis_data, family = poisson(link = "log"), 
                         offset = log_person_time_at_risk)
#write_rds(poisson_results, paste0(file_path, "Output/poisson_results.rds"))
```

```{r}
poisson_results <- read_rds(paste0(file_path, "Output/poisson_results.rds"))
summary(poisson_results)
#tidy(poisson_results, conf.int = TRUE)

poisson_simres <- simulateResiduals(poisson_results)
testDispersion(poisson_simres, alternative = "less")
plot(poisson_simres, rank = FALSE, quantreg = TRUE)
```

## Negative binomial model
```{r, echo=TRUE, eval=FALSE}
negbin_results <- glmer.nb(lrti_events_total ~ treatment_assigned + child_age + 
                           (1 | home:cohort:area) + 
                           offset(log_person_time_at_risk), 
                           data = analysis_data)
#write_rds(negbin_results, paste0(file_path, "Output/negbin_results.rds"))
```

```{r}
negbin_results <- read_rds(paste0(file_path, "Output/negbin_results.rds"))
summary(negbin_results)
#tidy(negbin_results, conf.int = TRUE)

negbin_simres <- simulateResiduals(negbin_results)
testDispersion(negbin_simres, alternative = "less")
plot(negbin_simres, rank = FALSE, quantreg = TRUE)
```

## Logistic regression model
```{r, echo=TRUE, eval=FALSE}
logreg_results <- glmer(lrti_events_di_total ~ treatment_assigned + 
                        child_age + person_time_at_risk +
                        (1 | home:cohort:area),
                        data = analysis_data, family = binomial, nAGQ = 20)
#write_rds(logreg_results, paste0(file_path, "Output/logreg_results.rds"))
```

```{r}
logreg_results <- read_rds(paste0(file_path, "Output/logreg_results.rds"))
summary(logreg_results)
#tidy(logreg_results, conf.int = TRUE)

logreg_simres <- simulateResiduals(logreg_results)
testDispersion(logreg_simres, alternative = "two.sided")
plot(logreg_simres, rank = FALSE, quantreg = TRUE)
```

```{r}
# Function to clean results
results_function <- function(model_results, model_name) {

tidy_results <- tidy(model_results, conf.int = TRUE) %>% 
  mutate(group_filter = if_else(grepl("treatment", term), 1, 0)) %>% 
  filter(group_filter == 1) %>% 
  mutate(term = gsub("treatment_assigned", "", term),
         model = model_name) %>% 
  dplyr::select(model, term, estimate, p.value, conf.low, conf.high)
tidy_results

}

# Run results through function, save, combine for plotting
poisson_tidy <- results_function(poisson_results, "Poisson")
negbin_tidy <- results_function(negbin_results, "Neg Bin")
logreg_tidy <- results_function(logreg_results, "Log Reg")

# Combine cleaned results
itt_results_combined <- rbind(poisson_tidy, negbin_tidy, logreg_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("Poisson", "Neg Bin", "Log Reg"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  ggtitle(label = "Results for ITT framework, LRTI outcome") +
  labs(y = "Estimate compared to placebo") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 45,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates

# Save plot as jpg
#ggsave("itt_plot_estimates.jpg", width = 12, height = 6)
```

# Interpretation:
As Jon and I discussed 11/16/20, the Poisson and Negative Binomial models appear to be
underdispersed (variance < mean), not overdispersed (variance > mean). These models 
don't appear to be the best fit for our data. Additionally, results from the models 
were essentially the same.  
The Logistic Regression model appears to be a better fit for the data (no concerns 
in the diagnostic plots). The good news is that the results were also very similar to 
the Poisson/NegBin models, so we don't have to explain any big differences in results 
if model selection concerns come up with reviewers. The bad news is that regardless 
of model, there is no difference in LRTI between treatment arms.   
Given these results, I'm leaning towards using the logistic regression model for the 
primary ITT framework. There are models that can be used for underdispersed count 
data (generalized Poisson regression?), but I can't find a good way to run those 
as mixed models like we need to do. I think the logistic regression model will be 
easier to explain/interpret, and we aren't really losing much information since there 
were so few children with 2+ cases of LRTI.

### 2020-11-18 stove_grade_usage_cleaning.Rmd
major analysis updates

kids_kw_report_clean <- kids_kw_report %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>%  
  arrange(area, home_winter_id) %>% 
  mutate(filter_type = fct_collapse(filter_type,
                                    "Honeywell" = "Honeywell",
                                    "Large Filtrete" = "Large Filtrete",
                                    "Small Filtrete" = "Small Filtrete",
                                    "Winix" = c("Winix", "winix"))) %>% 
  mutate(kw_perc_expected = if_else(kw_hours == -999, 999999, kw_perc_expected),
         kw_perc_expected = abs(kw_perc_expected)) %>% 
  replace_with_na(replace = list(kw_perc_expected = 999999)) %>% 
  mutate(kw_perc_expected = as.numeric(kw_perc_expected))

>>>>

kids_kw_report_clean <- kids_kw_report %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>%  
  arrange(area, home_winter_id) %>% 
  mutate(filter_type = fct_collapse(filter_type,
                                    "Honeywell" = "Honeywell",
                                    "Large Filtrete" = "Large Filtrete",
                                    "Small Filtrete" = "Small Filtrete",
                                    "Winix" = c("Winix", "winix"))) %>% 
  mutate(kw_perc_expected = if_else(kw_hours == -999, 999999, kw_perc_expected),
         kw_perc_expected = abs(kw_perc_expected)) %>% 
  replace_with_na(replace = list(kw_perc_expected = 999999)) %>% 
  mutate(kw_perc_expected = as.numeric(kw_perc_expected)) %>% 
  filter(treatment_assigned == "Filter")
